A Comprehensive Dataset of U.S. Federal Laws, 1789-2022

### 2023-11-08 draft/response.tex

\documentclass{article}
\usepackage[margins=1in]{geometry}

\begin{document}
\flushleft
\noindent Manuscript Number: SDATA-23-01716 \newline
\noindent Manuscript Title: A Comprehensive Dataset of U.S. Federal Laws, 1789-2022  \newline

Dear Dr. Jones and Anonymous Reviewers,

I thank you for the opportunity to revise the manuscript in light of this important feedback. I will respond to each reviewer in turn.

\subsection*{Reviewer 1}

\begin{itemize}

\item More Information On How To Use This Data

I thank the reviewer for this suggestion. The usage section is now significantly enhanced. Whereas previously the section had only one paragraph it now has four paragraphs that describes in much greater detail how the dataset might be used. In particular, I emphasize that one can use the dataset to conduct comparisons between some focus set to laws and those that are outside the focus (i.e. number of laws enacted during divided government versus unified government over time), and also as skeleton for constructing a dataset of laws with multiple labels where one wishes to understand the relationship between the labels (i.e. ``laws enacted during unified government'' and ``relative importance of the law"). Given the diversity of possible projects that scholars might have, the goal was not to describe every use case, but to give a general feel for the merging tasks that most scholars would typically follow.  I have clarified as well the confusing line 185-6.

\item How To Find Full Text of the Law

I thank the reviewer for this suggestion. At some point, I had considered including these texts in the data release, however for reasons I now elaborate in the draft this was a significant undertaking in its own right and something that I have left for later. The problem is basically that the public full texts are very limited in coverage, so one needs to use proprietary sources for the most part. These sources such as ProQuest and HeinOnline have digitized and scanned a lot of laws, but acquiring copies of these electronic versions in a comprehensive way is difficult. There is some possibility of using one government source, but it needs to be investigated.

Given that a comprehensive database of law \textit{texts} would be another project, the question as I understand it is how to go about finding the text of any particular law. This is not very difficult given that the citation system I use mirrors closely the table of contents of the original source documents, the statutes at large. I have typically included page numbers where available, so volume and page of statute at large is easily searched on HeinOnline and ProQuest. Where not available, one can use the table of contents of these volumes.

\item Figure Improvement

\end{itemize}
\subsection*{Reviewer 2}

\end{document}

### 2023-11-08 draft/v1.tex
added some response memo and so forth.

 Given the importance of U.S. federal lawmaking, it is surprising that no data source meets these goals of coverage and transparency. Yet it is worth detailing the numerous and painstaking data collection efforts that have come increasingly close. Some of the earliest existing data responsive to these criteria comes from a key debate in American political science about the consequences of divided government. In particular, scholars have wondered whether the state of unified government, where the President and Congress are controlled by the same party, is better or worse for legislative productivity than divided government, where these organs are not exclusively in controlled by the same political party. This debate was initiated by Mayhew (1991) \nocite{Mayhew1991}, who engaged this question quantitatively through a dataset of ``major'' legislative enactments. With slight simplification, Mayhew identified those pieces of legislation that were substantial through analyzing newspaper articles that summarized the achievements of the past legislative session, as we well as an examination of specialized historical works that retrospectively evaluated the importance of key pieces of legislation in a large number of policy areas. Mayhew's list of major enactments has been updated annually since its original publication in 1991 and is, at present writing, current from 1947 through 2022. Of course, this coverage of major legislative enactments is obviously limited as a database of all federal laws, both because it does not cover laws that fail to draw the attention of editorial pages, nor does it cover laws enacted during the New Deal or earlier.  Three issues implicit in Mayhew's pathbreaking data collection and analysis have continued to bedevil social scientists working in this area: transparency and reproducibility of inclusion or exclusion criteria, limited temporal coverage, and comprehensiveness within covered time-periods.

@@

The primary dataset we provide is publicly available at https://osf.io/qa289. Additionally, a Github repository that was used to construct the dataset will be made available upon publication.

@@

While we provide a numeric identifier that can be used for referring to particular rows of our dataset, we recommend that future researchers use identification for laws that reflect greater attention to the inconsistencies in citation practice over time. In particular,  we recommend matching efforts that use piece-wise rules as outlined in the methods section above and implemented via special merging functions in the git repository. Beginning with the 86th Congress laws should be matched using the public law number. Prior to the 56th Congress, laws should be matched by chapter number, Congress, and session. Finally, particular care needs to be paid in the matching of laws enacted between the 57th and 85th Congress. Generally, if public laws and chapters will be used to refer to laws in a dataset that is not exclusively relating to recent laws, one \textit{must} also include the Congressional session (or equivalently include the date of enactment, from which one can infer these details).

@@

All code used to create the dataset from original sources, is available through a Github repository made public upon publication. Also included in the repository are code and data used to validate the dataset as well as generate the figure. \footnote{\url{https://github.com/libgober/database_of_laws}}. Versions of these files used at time of submission to \textit{Scientific Data} are available in the OSF repository.

>>>>

 Given the importance of U.S. federal lawmaking, it is surprising that no data source meets these goals of coverage and transparency. Yet it is worth detailing the numerous and painstaking data collection efforts that have come increasingly close. My focus is on public, scholarly data collection efforts that produce the kinds of tables that are appropriate for statistical analysis, rather than proprietary databases such as ProQuest Congressional or HeinOnline which are designed with such access constraints that researchers cannot easily use their contents for many important research purposes or validate what these datasets deliver.\footnote{This is not to say that such proprietary databases are not useful. Indeed, we rely on source material from HeinOnline extensively. That said, these proprietary sources do not provide the sort of database described in this report.} Some of the earliest existing data responsive to these criteria comes from a key debate in American political science about the consequences of divided government. In particular, scholars have wondered whether the state of unified government, where the President and Congress are controlled by the same party, is better or worse for legislative productivity than divided government, where these organs are not exclusively in controlled by the same political party. This debate was initiated by Mayhew (1991) \nocite{Mayhew1991}, who engaged this question quantitatively through a dataset of ``major'' legislative enactments. With slight simplification, Mayhew identified those pieces of legislation that were substantial through analyzing newspaper articles that summarized the achievements of the past legislative session, as we well as an examination of specialized historical works that retrospectively evaluated the importance of key pieces of legislation in a large number of policy areas. Mayhew's list of major enactments has been updated annually since its original publication in 1991 and is, at present writing, current from 1947 through 2022. Of course, this coverage of major legislative enactments is obviously limited as a database of all federal laws, both because it does not cover laws that fail to draw the attention of editorial pages, nor does it cover laws enacted during the New Deal or earlier.  Three issues implicit in Mayhew's pathbreaking data collection and analysis have continued to bedevil social scientists working in this area: transparency and reproducibility of inclusion or exclusion criteria, limited temporal coverage, and comprehensiveness within covered time-periods.

@@

The primary dataset we provide is publicly available at \url{https://osf.io/qa289}. Additional data of interest used for validation is available within the files repository, available at \url{https://osf.io/mrghc}

@@

Our database presents a comprehensive table of U.S. laws. Depending on the research task, this table may receive different uses, and it is hard to anticipate all the places it will go. Having said that, we anticipate that scholars will frequently use this dataset by merging in some other dataset with labels, text, and so forth. Their research questions will presumably focus on the analysis of this meta-data about laws, possibly one at a time or perhaps in inter-relationship to one another. The research task about number of laws enacted during ``divided government" versus unified government is typical, for example, although perhaps too simple to see what the real challenge is because assigning the ``divided government" label requires the use of the ``date'' column. More challenging and typical would be adding labels that depend on individual identification of laws, for example the ``important" versus ``unimportant" distinction mentioned earlier. We presume that the scholar interested in our dataset has some set of laws $\mathcal{X}$ that they wish to merge to our data in order to compare laws that are in their set to laws that are outside their set. They would do so to illustrate what proportion of all laws their set of particular laws cover, for example, or to examine how some trends differ in their set versus outside their set differ. Often, scholars will have more than one set of laws that they are interested in, and their goal will be to setup a dataset involving sets of laws $\mathcal{X}$ and $\mathcal{Y}$. When working with multiple sets of partially overlapping lists of laws, it will often make sense to join both against a more comprehensive and universal set, as that keeps the scholars analytical options open. The basic question for using this data is what scholar needs to have in their source data to be able to use it.

On the one hand, we provide a numeric identifier that scholars can include to unambiguously refer to a particular federal law. Moreover, we outline a procedure that should lead to consistent numeric identification even by other scholars on a going forward basis. While providing this identifier is generally a good idea to remove doubt about what law one is referring to, we understand that adoption of our identifiers by other scholars cannot be presumed. Additionally, if procedures were to change or their were additions, amendments, or deletions to future versions of our dataset, then there would be questions about backward compatibility.

Therefore, in addition to referencing the identification system for laws we propose, we would also encourage scholars to pay attention to the citation systems as used in the source documents and record the necessary data accordingly. In particular, we recommend recording data and using matching based on the piece-wise rules as outlined in the methods section above and implemented via special merging functions in the git repository. Beginning with the 86th Congress laws should be matched using the public law number. Prior to the 56th Congress, laws should be matched by chapter number, Congress, and session. Finally, particular care needs to be paid in the matching of laws enacted between the 57th and 85th Congress. Generally, if public laws and chapters will be used to refer to laws in a dataset that is not exclusively relating to recent laws, one \textit{must} also include the Congressional session (or equivalently include the date of enactment, from which one can infer these details). While one often \textit{can} proceed to do matching without all these items, one runs a risk of problems, for example over-matching or mis-matching. More information such as bill title can certainly help to avoid ambiguities, but increasingly one will have a system of citation that is hard to make work across datasets.

Finally, a brief word on enriching these data with full texts of U.S. laws. This dataset does not provide the texts of laws that are listed, although doing so would be an appropriate extension of this work. What this data set does provide is citation information on publicly available source documents, so typically linking the text once found is no more challenging than any other linking of label task described above. That said, getting clean texts of law is very difficult on a consistent basis from public sources. Post-1995 laws in electronic text format are available from the US government printing office.\footnote{\url{https://www.govinfo.gov/app/collection/plaw}} These laws are formatted using markup that allows one to place footnotes correctly and also separate various formatting materials, although at present writing it is not clear how consistently these formats have been used over the years. Since 2013, laws are also available in an XML markup format. Earlier laws in the \textit{Statutes at Large} that are still provided by the US GPO as PDFs, although for most text data projects one would need to then OCR the documents and this generates familiar issues. In terms of comprehensive sources of earlier laws, HeinOnline provides full texts of all laws in both PDF and OCRed text format. Proquest Congressional covers the Statutes at Large between 1789 and 2014, and also offers PDFs.\footnote{\url{https://proquest.libguides.com/congressionalhelp/ccc}} The only comprehensive public source for obtaining law texts of which we are aware is a viewing tool provided by the Office of Revision Counsel,\footnote{To find 14 Stat. 41, for example, one can use this URL and it will generate an appropriate scan \url{https://uscode.house.gov/statviewer.htm?volume=14&page=41}} but the comprehensiveness of this data is untested at this point and the format is scanned PNGs rather than text or even PDF. Taking it as given that one can find the Statute at Large volume one wants, the citation information provided in the table is sufficient to conduct a table of contents search. Our data also does provide the page and volume number when readily available. Figure \ref{fig:toc} shows the table of contents of the statutes at large from both the "early" and "middle" citation regimes.

@@

All code used to create the dataset from original sources, validate the dataset, as well as generate the figures are available at OSF repository.\footnote{\url{https://osf.io/mrghc} }
